---
title: "EDA and Time Series Model Using AUBANK stock Dataset"
author: "AMAL JOSEPH"
date: "21/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### LOAD PACKAGES
```{r}

```

```{r, message=FALSE,warning=FALSE}
library(ggplot2)
library(ggthemes)
library(forecast)
library(tseries)
```

#### LOAD DATA

```{r, message=FALSE}
df <- read.csv("C:/Users/AMAL JOSEPH/Downloads/AUBANK.csv")
# Take a look at the class of the dataset US_candy_production
str(df)
```
```{r}
# variable names
colnames(df)
```
the attributes present in the dataset are:<br>
Open: Price of the stock when the market opens on a trading day
<br>
Close: Price of the stock when the market closes on a trading day
<br>
High: The highest value of the stock during that trading day
<br>
Low: The lowest value of the stock during that trading day
<br>
Adjusted Close: Closing price to reflect stock value after accounting for any corporate actions
<br>
Volume: Amount of shares traded over a trading day


```{r}
df$Date<-as.Date(df$Date)
```

```{r}
head(df)
```
```{r}
summary(df)
```
#### EDA

```{r}
library(ggplot2)

#create time series plot
p <- ggplot(df, aes(x=Date, y=Open)) +
       geom_line()

#display time series plot
p + scale_x_date(date_labels = "%b %Y")
```
```{r}


#create time series plot
p <- ggplot(df, aes(x=Date, y=Close)) +
       geom_line()

#display time series plot
p + scale_x_date(date_labels = "%b %Y")
```
```{r}


#create time series plot
p <- ggplot(df, aes(x=Date, y=High)) +
       geom_line()

#display time series plot
p + scale_x_date(date_labels = "%b %Y")
```
```{r}


#create time series plot
p <- ggplot(df, aes(x=Date, y=Low)) +
       geom_line()

#display time series plot
p + scale_x_date(date_labels = "%b %Y")
```
```{r}


#create time series plot
p <- ggplot(df, aes(x=Date, y=Volume)) +
       geom_line()

#display time series plot
p + scale_x_date(date_labels = "%b %Y")
```

```{r}
df%>%
  ggplot(aes(x = format(Date, "%m"), y = Volume)) +
      geom_bar(stat = "identity", fill = "darkorchid4")
```
```{r}
boxplot(df$Open~format(df$Date, "%m"),xlab="Month", ylab = "Open" ,main ="Monthly open stock value")
```
```{r}
boxplot(df$Close~format(df$Date, "%m"),xlab="Month", ylab = "Close" ,main ="Monthly Close stock value")
```
```{r}
boxplot(df$High~format(df$Date, "%m"),xlab="Month", ylab = "High" ,main ="Monthly High stock value")
```
```{r}
mean(df$Open)
```
